diffEnrich: An \proglang{R} Package to Compare Functional Enrichment Between Two Experimentally-derived Groups of Genes by Connecting to the KEGG REST API

### 2020-04-06 jss-article-rnw-diffEnrich/article.Rnw
Addded parameter descriptions for pathEnrich to app note

>>>>

\begin{table}[]
\centering
  \caption{\label{tab:description} Description of parameter usage for \code{pathEnrich}.}
  \begin{adjustbox}{width=\textwidth}
\begin{tabular}{lll}
\hline
\textbf{Argument} & \textbf{Description}                                                                                                                                                                                                                                                                                                                                                                                                            & \textbf{Example}      \\
\hline
gk\_object        & \begin{tabular}[c]{@{}l@{}}list. Object genrated from get\_kegg, or a list containing the output \\ generated from a past get\_kegg call. Names of the list must match \\ those defined in get\_kegg. If the user wishes to use an older version\\  of data generated by get\_kegg, they must first load that data and\\  put it in a named list that matches the names given in the list \\ generated by get\_kegg.\end{tabular} & gk\_obj = kegg        \\
gene\_list        & \begin{tabular}[c]{@{}l@{}}Vector. Vector of NCBI (ENTREZ)\\  geneIDs.\end{tabular}                                                                                                                                                                                                                                                                                                                                               & gene\_list = yourList \\
method            & \begin{tabular}[c]{@{}l@{}}Character. Character string telling diffEnrich which method to \\ use for multiple testing correction. Available methods are \\ those provided by p.adjust, and the default is "BH", or \\ False Discovery Rate (FDR).\end{tabular}                                                                                                                                                                    & method = "BH"         \\
cutoff            & \begin{tabular}[c]{@{}l@{}}Numeric. The p-value threshold to be used as the cutoff when\\  determining statistical significance, and used to filter list\\  of significant pathways.\end{tabular}                                                                                                                                                                                                                                 & cutoff = 0.05         \\
N                 & \begin{tabular}[c]{@{}l@{}}Numeric. The number of genes from the gene list that must\\  be present in a KEGG pathway in order for that pathway \\ to be retained and tested.\end{tabular}                                                                                                                                                                                                                                         & N = 2
\end{tabular}
\end{adjustbox}
\end{table}
